\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-26 papers/jfp/5-rebuilders.tex
Link in the Shake precision in this paper
Minor tweaks

\begin{minted}[fontsize=\small,xleftmargin=10pt]{haskell}
recordVT@\,@::@\,@k -> Hash v -> [(k, Hash v)] -> VT k v -> VT k v
verifyVT@\,@::@\,@(Monad m,@\,@Eq k,@\,@Eq v) => k -> Hash v -> (k -> m (Hash v)) -> VT k v -> m Bool
\end{minted}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
data Trace k v = Trace { key :: k, depends :: [(k, Hash v)], result :: Hash v }
\end{minted}

@@

\subsubsection{Step Verifying Traces}

>>>>

\begin{minted}[fontsize=\small,xleftmargin=10pt]{haskell}
recordVT :: k -> Hash v -> [(k, Hash v)] -> VT k v -> VT k v
verifyVT :: (Monad m, Eq k, Eq v)
         => k -> Hash v -> (k -> m (Hash v)) -> VT k v -> m Bool
\end{minted}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
data Trace k v = Trace
    {key :: k
    ,depends :: [(k, Hash v)]
    ,result :: Hash v
    }
\end{minted}

@@

\subsubsection{Verifying Step Traces}\label{sec-step-traces}

### 2019-04-26 papers/jfp/7-experience.tex
Minor tweaks

\begin{minted}[xleftmargin=10pt]{haskell}
data Action k v = Finished v
                | Depends v (v -> Action)
\end{minted}

@@

Once again, this type is isomorphism to \hs{Task Applicative}. By describing these types using \hs{Task} we are able to pinpoint the differences (\hs{Monad} vs \hs{Applicative}) and use existing literature to prove what is and isn't possible.

>>>>

\begin{minted}[xleftmargin=10pt]{haskell}
data Action k v = Finished v
                | Depends v (v -> Action k v)
\end{minted}

@@

Once again, this type is isomorphiv to \hs{Task Applicative}. By describing these types using \hs{Task} we are able to pinpoint the differences (\hs{Monad} vs \hs{Applicative}) and use existing literature to prove what is and isn't possible.
